# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data


```{r}
activity=read.csv("activity.csv")
activity2=activity[complete.cases(activity),]

```

## What is mean total number of steps taken per day?

```{r}
byday=aggregate(activity2[,1],list(activity2[,2]),FUN=sum)
hist(byday[,2],breaks=20)
meanbyday=format(round(mean(byday[,2])),scientific = FALSE)
medianbyday=format(round(median(byday[,2])),scientific = FALSE)

```

There are is an average of `r meanbyday` steps per day and a median of `r medianbyday`. 

## What is the average daily activity pattern?

```{r}
by5min=aggregate(activity2[,1],list(activity2[,3]),FUN=mean)
plot(by5min[,2],type="l")
maxby5min=by5min[which(by5min[,2]==max(by5min[,2])),1]
```

The maximum average 5 minute interval is `r maxby5min`.   

## Imputing missing values
```{r}
avg5min=rep(by5min[,2],61)
avg5min=avg5min[1:nrow(activity)]
activity2a=activity
activity2a[is.na(activity2a[,1]),1]=avg5min[is.na(activity2a[,1])]
bydaya=aggregate(activity2a[,1],list(activity2a[,2]),FUN=sum)
hist(bydaya[,2],breaks=20)
meanbydaya=format(round(mean(bydaya[,2])),scientific = FALSE)
medianbydaya=format(round(median(bydaya[,2])),scientific = FALSE)
```

There are is an average of `r meanbydaya` steps per day and a median of `r medianbydaya`. This is not that different from the non imputed data.




## Are there differences in activity patterns between weekdays and weekends?
```{r}
dayofweek=weekdays(as.Date(activity[,2]))
activity2b=activity2a
activity2b[,4]="Weekday"
activity2b[(dayofweek %in% c("Saturday","Sunday")),4]="Weekend"
#byweekend=aggregate(activity2b[,1],list(activity2b[,4]),FUN=mean)
activity3=split(activity2b,activity2b[,4])
activity3a=data.frame(activity3[1])
activity3b=data.frame(activity3[2])

by5min2a=aggregate(activity3a[,1],list(activity3a[,3]),FUN=mean)
by5min2b=aggregate(activity3b[,1],list(activity3b[,3]),FUN=mean)
par(mfrow = c(2, 1))

plot(by5min2a,type="l",main="Weekdays",xlab="Interval")
plot(by5min2b,type="l",main="Weekends",xlab="Interval")
dev.off()


```



